% LaTeX resume using res.cls

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage[bookmarks=true,pdfborder={0 0 0}]{hyperref}
%\usepackage{hyperref}

\usepackage[colorlinks]{hyperref}
\hypersetup{urlcolor=blue}
\usepackage[svgnames]{xcolor}

\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
% Draw a horizontal line the whole width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Parag Gupta}
 % Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 
\address{114, Old Boys Hostel\\
International Institute of Information Technology \\
Gachibowli, Hyderabad - 500032 \\
Andhra Pradesh, India. \\
Contact Number : +91-7416524684 }

\address{University Roll Number : 201001125 \\
\hypersetup{urlcolor=Maroon}
Email : \href{mailto:paraggupta1993@gmail.com}{paraggupta1993@gmail.com} \\
\hypersetup{urlcolor=blue}
GitHub: \href{https://github.com/paraggupta1993}{github.com/paraggupta1993} \\
Profile: \href{http://www.linkedin.com/in/darkhorcrux}{linkedin.com/in/darkhorcrux} \\
Date Of Birth : March 20, 1993 \\
}

\begin{resume}
 
\section{Education} {\sl \bf Bachelor of Technology,} Computer Science and Engineering    \hfill{2010-2014}\\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
		  \hypersetup{urlcolor=black}          
          \href{http://www.iiit.ac.in/}{International Institute of Information Technology - Hyderabad} \\
		  \hypersetup{urlcolor=blue}
          Current status : 4th year ( 7th semester ) \\
          {\bf CGPA : 7.75 / 10}
                 
          {\sl Senior Secondary schooling ,} Class ${12}^{th}$   \hfill{2009-2010} \\
		  \hypersetup{urlcolor=black}          
          \href{http://www.morningstarratlam.com/home_morningstarschool.htm}{Morning Star Higher Secondary School}, Ratlam , India \\
          \hypersetup{urlcolor=blue}
          Percentage : 90.8 \% 


\section{Interest} { Web development, Algorithms, Problem solving, Computer Networks, Data and Knowledge extraction. }


\section{Experience}
{\sl \underline{\bf Internships} : }
\begin{itemize}
\item
 \hypersetup{urlcolor=black}
 {\it \href{http://www.linkedin.com/company/groupon-india}{Groupon India Private Limited}} \hfill{Summer 2013} \\
 \hypersetup{urlcolor=blue}

 Developed an internationalized and localized web application, internally used by the company over 40+ countries to enhance {\it customer relationship management.} \hfill{Developers team size: 4} 
\item
\hypersetup{urlcolor=black}
{\it \href{http://www.linkedin.com/company/3049433}{Aasaanpay Solutions India Private Limited}}  \hfill{Spring 2013}
\hypersetup{urlcolor=blue}
 Setted-up PCI complaint infrastructure on cloud and developed user interface for the company's android application.   
\end{itemize} 

{\sl \underline{\bf Teaching Assistant} at IIIT-Hyderabad: } 
\begin{itemize}
\item IT Workshop  \hfill{Monsoon 2013}
\item Computer System Organization \hfill{Spring 2013}
\item Structured Systems Analysis and Design \hfill{Monsoon 2012}
\end{itemize}



\section{Achievements}

\begin{itemize}
\item
	\hypersetup{urlcolor=black}	
	\href{http://icpc.baylor.edu/}{ACM - International collegiate programming contest}, Asia Regionals \\
	\hypersetup{urlcolor=blue}
	{(Team size: 3)}
	\begin{itemize}
		\item 15 rank, Kanpur     \hfill{2012-2013} 
		\item 22 rank, Amritapuri \hfill{2012-2013}
		\item 21 rank, Amritapuri \hfill{2011-2012} 
	\end{itemize}	 

\item Rank 3316 in IIT-JEE and Rank 2026 in AIEEE \hfill{2010}
\item IIIT-Hyderabad Dean's award I and II for academic excellence. \hfill{2010-2011} 
\end{itemize}


\section{Major Projects}
{\bf Information Leak using ICMP protocol} \hfill{Mentor: \href{http://iiit.ac.in/people/faculty/shatrunjay.rawat}{Shatrunjay Rawat}}  \\
$\rightarrow$ {\it C, Python, Computer networks, pthreads, BSD Sockets } \\
This project aims at transferring data packets using ICMP protocol. Study the security loopholes associated with ICMP and measures to prevent any such security attacks. (Use of wire-shark, Iptables, ICMP tunneling, etc.)  \hfill{(Team size: 2)}

{\bf Entity Based Opinion Mining from Blogs} \hfill{Mentor: \href{http://faculty.iiit.ac.in/~vv/Home.html}{Vasudev Verma}} \\
$\rightarrow$ {\it Java, Eclipse, Stanford NLP toolkit, Sentiment Analysis, Opinion Mining, Object Identification, Opinion Summary
} \hfill{(Team size: 2)} \\
It attempts to identify objects being
talked about in the blog and the opinion(sentiment) that the author expresses
towards them which can further be summarized. 
Based on {\it "Entity Centric Opinion Mining from Blogs"} published in Coling-2012. 

{\bf Wikipedia Search Engine} \hfill{Mentor: \href{http://faculty.iiit.ac.in/~vv/Home.html}{Vasudev Verma}} \\
$\rightarrow$ {\it CPP/C++ , Python, Bash script, Information extraction, XML, Tf-idf } \\
Designed a scalable and efficient wikipedia dataset search engine.It supports field queries for 5 fields: title, infobox, outlinks, category and content.It builds multi-level indexes. Total index-size was $< 1/4^{th}$ for $40 GB$ dataset, answering queries in $ < 1s$. 

{\bf Compiler Optimization Phase Sequence Search Engine} \\
$\rightarrow$ {\it Python, GCC, llvm, Hill Climbing algorithm (heuristic search) } \\
{ Mentor: \href{http://iiit.ac.in/people/faculty/psuresh}{Suresh Purini}} \\
It aims to find out optimal compilation phase sequence for llvm and gcc compilers irrespective of input and the program. It performed at par with $-O2$ optimization sequence of gcc compiler.  



\section{Minor Projects}
{\bf API addition in OpenStack Nova-Client} \hfill{Mentor:Prasad Saripalli} \\
$\rightarrow$ {\it Python, OpenStack, Cloud,  libvirt, Virtualization } \\
OpenStack is a Cloud operating system. Added an API in Nova-client of Openstack using libvirt to dynamically add/remove memory from live Virtual machines.

{\bf Room Reservation Web Application} \hfill{Mentor: \href{http://faculty.iiit.ac.in/~raghu.reddy/Home.html}{Y Raghu Reddy}} \\ 
$\rightarrow$ {\it PHP, HTML, CSS, AJAX, Javascript, Web development } \\
Built and deployed web application for room booking in IIIT-Hyderabad. \hfill{(Team size: 5)}

{\bf Proxy Web Server} \hfill{Mentor: \href{http://iiit.ac.in/people/faculty/bezawada}{Bezawada Bruhadeshwar}} \\ 
$\rightarrow$ {\it C, BSD Sockets, computer networks, pthreads, caching} \\
Developed a TCP based proxy web server that serves HTTP requests with a cache replacement policy.




\section{
Skill Set}

\begin{table}[htbp]
\begin{tabular}[ht]{|l | p{7cm} |}
\hline
Operating system & Linux/Unix, Microsoft Windows, OS X \\
\hline
Languages & C, C++, Python, Ruby, PHP, Javascript, Scheme, Latex, Bash, Java, ARM-assembly \\
\hline
DBMS & Mysql \\
\hline
Programming Environment & Vim, eclipse, Sublime Text \\
\hline
Web Development & HTML, CSS, Web2py, Ruby on Rails, Backbone, Jquery, Bootstrap \\
\hline
API's/softwares
& Amazon AWS(S3, EC2),
Openstack, REST, Wireshark, Cisco Packet Tracer,
OpenGL, Pthread, Libvirt, Git \\
\hline

\end{tabular}
\end{table}

\section{Relevant courses}
Advanced Computer Networks, Parallel Programming, Compilers, Computer System Organization, Operating systems, Programming languages, Data structures and Algorithms, Structured system analysis and design, Information Retrieval and Extraction, System Resource Virtualization, Database management Systems, Dataware housing and data mining.


\section{Extra-Curricular \\ Activities}
{\it Cultural Advisor,} IIIT-Hyderabad \hfill{2013-Present} \\
{\it Cultural Secretary,} IIIT-Hyderabad  \hfill{2012 - 2013} \\
{\it Coordinator,} IIIT-Hyderabad's chapter of {\it Spic-Macay} \hfill{2012 - 2013} \\
{\it Dance Club Head,} IIIT-Hyderabad \hfill{2011 - 2013}
            
\noindent The above information is correct to the best of my knowledge.\\
Updated on : September 17, 2013 \hfill{- Parag Gupta} 


\end{resume}


\end{document}




